\racets: Faceted Execution in Racket

### 2018-07-24 paper/paper.tex
fixing \lang

\documentclass[review=true,acmlarge]{acmart}

@@

\newcommand{\comm}[3][\color{red}]{{#1{[{#2}: {#3}]}}}
\newcommand{\zw}[1]{\comm[\color{green!66!black}]{Zhanpeng}{#1}}
\newcommand{\kris}[1]{\comm[\color{blue}]{Kris}{#1}}
\newcommand{\tom}[1]{\comm[\color{orange}]{Tom}{#1}}
\newcommand{\lang}[0]{$\lambda_\textsc{FE}$\xspace}
\newcommand{\racets}[0]{$\textsc{Racets}$\xspace}
\newcommand{\facet}[3]{{\fcol{\ensuremath{\langle \, {#1} \: ? \: {#2} \diamond \: {#3} \, \rangle}}}}
\newcommand{\formfacet}[3]{{\fcol{\ensuremath{\langle \langle \, {#1} \: ? \: {#2} \diamond \: {#3} \,  \rangle \rangle}}}}
\newcommand{\var}[1]{\mathit{#1}}

@@

\begin{lstlisting}[language=Racket,escapechar=|,name=rebindingexample]
(define alice-label (let-label l (lambda (x) (= x alice)) l))
(define x (fac alice-label 1 0))
(let ([alice-label (let-label l (lambda (x) true) l)]) |\label{lineno:alicelab}|
  (obs alice-label 1 x)) ; Should return |\facet{\texttt{alice-label}}{1}{0}|
\end{lstlisting}

@@

\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=other,numbers=none]
(fac l true (error ''this shouldn't get evaluated if <@\bmth{+\ell \in pc}@>''))
\end{lstlisting}

@@

\begin{figure}
{\small
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets]
(define-syntax-rule (fac l e1 e2)
  (cond
\end{lstlisting}
\vspace{-.7\baselineskip}
{\color{brown}
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{brown}]
    [(set-member? (current-pc) (pos (facet-labelname l))) e1]
\end{lstlisting}
}
\vspace{-.7\baselineskip}
{\color{gray}
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{gray}]
    [(set-member? (current-pc) (neg (facet-labelname l))) e2]
\end{lstlisting}
}
\vspace{-.7\baselineskip}
{\small\color{purple}
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{purple},keywordstyle=\color{purple}]
    [else
     (let ([left (parameterize
                     ([current-pc (set-add (current-pc)
                                           (pos (facet-labelname l)))]))]
           [right (parameterize
                      ([current-pc (set-add (current-pc)
                                            (neg (facet-labelname l)))]))])
           (mkfacet (set-union (set (pos (labelpair-name l)))
                                    (current-pc))
                    v1 v2))]))
\end{lstlisting}}
}
\caption{Facet creation as a macro}
\label{fig:fac-create}
\end{figure}

@@

\begin{lstlisting}[language=Racket,escapechar=|,name=case]
(define p1l (mkpol "player1"))
(define p1board
  (box (fac p1l
            (add-pieces (makeboard) '(1 2 ldots))
            (makeboard))))
\end{lstlisting}

>>>>

\documentclass[acmlarge]{acmart}

@@

%% \newcommand{\comm}[3][\color{red}]{{#1{[{#2}: {#3}]}}}
%% \newcommand{\zw}[1]{\comm[\color{green!66!black}]{Zhanpeng}{#1}}
%% \newcommand{\kris}[1]{\comm[\color{blue}]{Kris}{#1}}
%% \newcommand{\tom}[1]{\comm[\color{orange}]{Tom}{#1}}
\newcommand{\lang}[0]{$\lambda_\textsc{FE}$\xspace}
\newcommand{\racets}[0]{$\textsc{Racets}$\xspace}
\newcommand{\facet}[3]{{\fcol{\ensuremath{\langle \, {#1} \: ? \: {#2} \diamond \: {#3} \, \rangle}}}}
\newcommand{\formfacet}[3]{{\fcol{\ensuremath{\langle \langle \, {#1} \: ? \: {#2} \diamond \: {#3} \,  \rangle \rangle}}}}
\newcommand{\var}[1]{\mathit{#1}}

@@

\begin{lstlisting}[language=Racket,escapechar=|,name=rebindingexample]
(define alice-label (let-label l (lambda (x) (= x alice)) l))
(define x (facet alice-label 1 0))
(let ([alice-label (let-label l (lambda (x) true) l)]) |\label{lineno:alicelab}|
  (obs alice-label 1 x)) ; Should return |\facet{\texttt{alice-label}}{1}{0}|
\end{lstlisting}

@@

\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=other,numbers=none]
(facet l true (error ''this shouldn't get evaluated if <@\bmth{+\ell \in pc}@>''))
\end{lstlisting}

@@

\begin{figure}
{\small
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets]
(define-syntax-rule (facet l e1 e2)
  (cond
\end{lstlisting}
\vspace{-.7\baselineskip}
{\color{brown}
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{brown}]
    [(set-member? (current-pc) (pos (facet-labelname l))) e1]
\end{lstlisting}
}
\vspace{-.7\baselineskip}
{\color{gray}
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{gray}]
    [(set-member? (current-pc) (neg (facet-labelname l))) e2]
\end{lstlisting}
}
\vspace{-.7\baselineskip}
{\small\color{purple}
\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{purple},keywordstyle=\color{purple}]
    [else
     (let ([left (parameterize
                     ([current-pc (set-add (current-pc)
                                           (pos (facet-labelname l)))]))]
           [right (parameterize
                      ([current-pc (set-add (current-pc)
                                            (neg (facet-labelname l)))]))])
           (mkfacet (set-union (set (pos (labelpair-name l)))
                                    (current-pc))
                    v1 v2))]))
\end{lstlisting}}
}
\caption{Facet creation as a macro}
\label{fig:fac-create}
\end{figure}

@@

\begin{lstlisting}[language=Racket,escapechar=|,name=case]
(define p1l (mkpol "player1"))
(define p1board
  (box (facet p1l
            (add-pieces (makeboard) '(1 2 ldots))
            (makeboard))))
\end{lstlisting}
